# Data
## Technical description

## Research plan

## Missing value analysis
### First load our dataset:
```{r}
arrest_juvenile = read.csv("preprocessing/arrests_national_juvenile.csv")
arrest_adults = read.csv("preprocessing/arrests_national_adults.csv")
hate_crime22 = read.csv("preprocessing/hate_crime_2022.csv")
```
### Use aggregated missing patterns to check missing values in each dataset:
**Arrest_juvenile**
```{r}
#| fig-width: 50
#| fig-height: 25
#| out-width: 80%
library(redav)
library(ggplot2)
plot_missing(arrest_juvenile, percent=FALSE)+
  theme_bw(5)
```
The column "state_abbr" (state abbreviation)is completely missing. Unfortunately, we couldn't find other datasets which perfectly make up for the lack of state abbreviation. Since our main goal is not about discovering arrest crimes in states, we decide to drop "state_abbr" column. We have several missing values in "american_indian" and "asian_pacific_islander", which are more likely to be missing due to "not all agencies report race and/or ethnicity for arrests" from the FBI. We also have missing values in "f_0_9", f_0_12", "m_0_9", "f_13_14", "f_15", "m_10_12", "f_16" in decreasing order. Even though "all agencies must report age and sex", it is hard to implement in reality, and some agencies might not consistently report data which lead to missing values. Since missing values are not correlated with other variables and take up only a small percent, we would drop rows with missing values.

**Arrest_adults**
```{r}
#| fig-width: 70
#| fig-height: 25
#| out-width: 80%
plot_missing(arrest_adults, percent=FALSE)+
  theme_bw(5)
```

Similarly, the column "state_abbr" (state abbreviation)is completely missing. This time, we have fewer columns with missing values, only "f_60_64", f_65_p", "f_55_59" in decreasing order. In other words, we can see missing values are concentrated in females aged between 55 to 65+. The interesting pattern might caused by certain oversight when reporting elderly women in the agencies. Since missing values are not correlated with other variables and take up only a small percent, we would drop rows with missing values.

**Hate Crime**
```{r}
#| fig-width: 60
#| fig-height: 25
#| out-width: 80%
plot_missing(hate_crime22,percent=FALSE)+
  theme_bw(5)
```

We have equal number of missing values in "adult_offender_count" and "juvenile_offender_count". They are correlated because in each hate crime incident, agencies either report all the offenders, or they fail to report. The number of missing value of "juvenile_victim_count" is slightly higher than "adult_victim_count". One of the possible explanation is that the agencies are more likely to protect the privacy of juvenile that they choose not to report in the reality. We also have missing values in "total_individual_victims", given "total_individual_victims" is likely correlated with "juvenile_victim_count" and  "adult_victim_count". Since for **Hate Crime**, we are more interested in the "location, offender race and bias type" instead of the number of offenders and victims, we could subset the dataset to drop the columns with missing values.
